---
title: "Over/Under Betting Strategy"
author: "by [Benjamin DAVID]()"
mail: benjamin7david@gmail.com
output:
  epuRate::epurate:
    code_folding: show
    number_sections: no
    toc: yes
  html_document:
    df_print: paged
    toc: yes
logo: logo_gallery.png
---

<style>
#TOC {
top: 1%;
opacity: 0.5;
}
#TOC:hover {
opacity: 1;
}
</style>


> Challenge presentation : The main goal is to formulate an over/under betting strategy based on the football_example csv file. To do so, we will predict the profit using a machine learning approach. We determine Prediction Intervals with Quantile Regression Forests (Random Forests) and use them to formulate our strategy. 

> **METHODOLOGY** ------- 
<br><br>
1. Identify the type of problem : supervised learning or unsupervised learning ? regression or classification ? Define a error metric to compare models.
<br> The challenge is a **regression problem** and the **Mean Absolute Error (MAE)** will be the metric to evaluate the performance.
<br><br>
2. **Data understanding** - missing values, variable types (One hot encoding : Many models require all variables to be numeric) - Handle missing values if necessary (delete rows or mean/median imputations).
<br><br>
3. **Descriptives statistics** - response variable distribution. Main statistics (min, max, mean, quantiles, standard deviation, mode (for categorical variables)) for each feature.
<br><br>
4. **Correlation analysis** between response variable and other numeric variables (or categorical variables after one hot encoding)
<br><br>
5. **Data Splitting** : training set (used to train algorithms and tune hyper-parameters) and testing set (used to estimate its prediction error (generalization error)). Data from test set won't be used during model training.
<br><br>
6. **Cross validation** on the training set in order to define the best strategy.
<br> Comparison of different algorithms (OLS, Ridge, Lasso, ... Random Forest, XGBoost) by tuning the hyper-parameters in the cross validation.
<br><br>
7. **Identify the best strategy** by analyzing the cross validation errors for each model. 
<br><br>
8. **Retrain** the best model (i.e model with best hyper-parameters from cross validation) **on the full training set** & **assess performance on the testing set**.
<br> In the following code, we'll tune some hyper-parameters in the cross validation but without seeking for the optimal combination (grid search).
<br><br>
9. **Formulate a over/under betting strategy** based on quantile predictions from Random Forest. Check the **performance and the robustness of the strategy**


***
**LOAD PACKAGES**

```{r setup, message = FALSE, warning = FALSE, echo = TRUE, eval = TRUE}

# Disable scientific notation 
options(scipen=999)

# Load useful packages ----

# Data manipulation
library(tidyverse)
library(data.table)
library(broom)

# String manipulation
library(stringr)

# Resample data 
library(rsample)
library(recipes)

# Correlation Analysis 
library(correlationfunnel)

# Machine learning
library(caret)
library(mlr)
library(glmnet)
library(gbm)
library(xgboost)
library(e1071)
library(neuralnet)
library(kernlab)
library(rpart)
library(ranger)
library(randomForest)
library(splines)

# Graphics 
library(ggplot2)
library(plotly)

# Data Cleaning
library(janitor)

# EDA 
library(skimr)

# Apply mapping functions 
library(purrr)
library(furrr) # in parallel 

# Rmarkdown 
library(epuRate)
library(rmarkdown)
library(knitr)
library(formattable)
library(kableExtra)

# TIming R scripts
library(tictoc)

```


***
# EXPLORATION DATA ANALYSIS
```{r, message = FALSE, warning = FALSE, echo = TRUE, eval = TRUE}
# # Exploring data 
# summarize_df<- mlr::summarizeColumns(df)

# there are some algorithms which don’t require you to impute missing values
# You can simply supply them missing data. They take care of missing values on their own
# Let’s see which algorithms are they
# listLearners("regr", check.packages = TRUE, properties = "missings")[c("class","package")]

# To get the list of parameters for any algorithm
# getParamSet("regr.cvglmnet")

# Import data from Github 

link_github <- "https://raw.githubusercontent.com/benj7/betting_strategy/master/football_example.csv"

df <- fread(link_github)
# 38,810 rows and 22 variables 

# back up data initial 
df_backup <- df

```

## Descriptive Statistics

```{r, message = FALSE, warning = FALSE, echo = TRUE, eval = TRUE}

# Descriptive stats 
skim(df)

```

<br><br>

> It's very interesting to notice that the profit mean is negative: -0.0443. **If we decide to place all bets, the overall profit is negative, equals to -1721.**

> The variable "home_score" and "away_score" which are the score at the 15th minute for home and away teams are always equal to 0. This variable is not reliable enough to be used for modelling. 


## Response Variable Distribution

```{r, message = FALSE, warning = FALSE, echo = TRUE, eval = TRUE}

plot_ly(data = df, 
        x = ~profit,
        type = "histogram",
        histnorm = "probability") %>%  
  layout(title = "Frequency distribution of Profit",
         xaxis = list(title = "Profit",
                      zeroline = FALSE),
         yaxis = list(title = "Frequency",
                      zeroline = FALSE))


```

<br>
> **Around 54% of the bets have a profit negative or equals to 0.**
<br> 
The response variable is skewed but we can't consider log transformation since the target can be negative 


# CORRELATION ANALYSIS 

> Correlation Analysis on data that has been preprocessed to identify key features that relate to the target

```{r, message = FALSE, warning = FALSE, echo = TRUE, eval = TRUE}

# Feature Engineering ----

df <- df %>% mutate(
  
  # Rename modalities of the variable "selection"
  selection = case_when(selection == "home" ~ "over",
                        selection == "away" ~ "under"),
  
  # Compute difference between elo_home and elo_away
  elo_diff_ft = elo_home_ft - elo_away_ft,
  
  elo_diff_fh = elo_home_fh - elo_away_fh,
  
  # Compute difference between league_prod_at_least and implied probability from odds 
  diff_probs = league_prob_at_least - 1/(odds+1),
  
  # Total number of goals
  nb_goals = final_home_score + final_away_score,
  
  # Is profit positive? 1: Yes - 0:No
  positive_profit = if_else(profit > 0, 1, 0),
  
  # Ratio between profit and odds 
  profit_odd_ratio = profit/odds)

df <- as.data.table(df)

df <- df[profit < 0, profit_odd_ratio := profit]

# Round numeric variables to 3 decimal
col_num <- which(sapply(df,class) == "numeric")

sdcols <- names(df)[col_num]
  
df_num <- df[, lapply(.SD, function(x) round(x,3)), .SDcols = sdcols]

df_no_num <- df[, .SD, .SDcols = setdiff(names(df), sdcols)]

df <- cbind(df_no_num, df_num)

# Correlation Analysis - Identify key features that relate to the target ("profit")

# Transform the data into a binary format 
df_binarized <- df %>%
  # remove useless variables with no information or variables that we don't know before betting 
  select(-c(market_id, 
            match_start_time_gmt, 
            league_id, 
            home, 
            away,
            home_score,
            away_score, 
            observations,
            minute,
            final_home_score,
            final_away_score,
            minute,
            nb_goals,
            profit,
            profit_odd_ratio)) %>%
  binarize(n_bins = 5, thresh_infreq = 0.01, name_infreq = "OTHER", one_hot = TRUE)

# Perform correlation analysis 

df_binarized_corrl <- df_binarized %>%
  correlate(positive_profit__1)

# Visualize the feature-target relationships

df_binarized_corrl %>%
  plot_correlation_funnel()

```


> Low odds are logically more correlated with a positive profit.  According to this analysis, the "diff_probs" feature seems to be correlated with the profit - this is interesting for modelling purposes! 

```{r, message = FALSE, warning = FALSE, echo = TRUE, eval = TRUE}

# Remove useless variables with no information or variables that we don't know before betting 
df <- as.data.table(df)

features_to_keep <- setdiff(names(df),c("market_id",
                                        "match_start_time_gmt",
                                        "league_id", 
                                        "home", 
                                        "away",
                                        "home_score",
                                        "away_score", 
                                        "observations",
                                        "minute",
                                        "final_home_score",
                                        "final_away_score",
                                        "minute",
                                        "nb_goals",
                                        "positive_profit",
                                        "profit_odd_ratio"))

df_model <- df[, .SD, .SDcols = features_to_keep]

# one-hot encode our categorical variables
one_hot <- dummyVars(~ ., df_model, fullRank = FALSE)
df_model_hot <- predict(one_hot, df_model) %>% as.data.frame()

```

***
# MODELING
## Data Splitting 

```{r, message = FALSE, warning = FALSE, echo = TRUE, eval = TRUE}

# Response variable renaming  
df_model_hot <- df_model_hot %>%
  rename(Y = profit)

# Separate into random training and test data sets ----

# set.seed() for reproducibility 
set.seed(123) 

# We keep 80% of the data for model training 
split_strat <- initial_split(df_model_hot, prop = 0.8)
df_train  <- training(split_strat)
df_test   <- testing(split_strat)

```

br><br>
> We implement a 5-fold cross validation manually (for loop)
<br>
This gives us a lot of flexibility and provides a good understanding of what goes on behind the scenes.
<br> 
For large-scale machine learning projects, I use H2O which automates the cross validation and hyperparameter tuning process. It's much faster and more scalable since H2O is written in Java. 

## 5-fold Cross validation implementation on the training set
```{r, message = FALSE, warning = FALSE, echo = TRUE, eval = TRUE}
# Training set 
X <- as.data.table(df_train %>% select(-Y))
Y <- df_train$Y

XY <- cbind(Y,X)
names(XY)[1] <- "Y"

# Testing set 
X_test <- as.data.table(df_test %>% select(-Y))
Y_test <- df_test$Y

XY_test <- cbind(Y_test, X_test)
names(XY_test)[1] <- "Y"

# Cross validation 
# Higher CV metrics determine that our model does not suffer from high variance and generalizes well on unseen data

# Number of folds
N <- 5

# Folds building
set.seed(123)
Folds <- sample(1:dim(XY)[1] %% N + 1)

Output <- list()
Time <- list()

i <- 1

# for loop to perform cross validation 
for(i in 1:N){
  Predictions <- list()
  
  # Estimation samples
  XE <- X[Folds != i]
  YE <- Y[Folds != i]
  # Data needs to be in a matrix format for some models 
  XME <- as.matrix(XE)
  YME <- as.matrix(YE)
  XYE <- XY[Folds != i]
  
  # Prediction samples 
  XP <- X[Folds == i]
  YP <- Y[Folds == i]
  # Data needs to be in a matrix format for some models 
  XMP <- as.matrix(XP)
  YMP <- as.matrix(YP)
  XYP <- XY[Folds == i]
  
  print(stringr::str_c("Fold number ", i))
  print("**************************************************")
  
  # Add the Y variable to the prediction dataset (for comparison purpose)
  Predictions[["Y"]] <- YP
  Predictions[["Y"]] <- as.numeric(Predictions[["Y"]])
  
  #********************* ORDINARY LEAST SQUARES **********************#
  
  print(Nom <- "OLS (LM)")
  Start <- proc.time()
  Model <- stats::lm(formula = Y ~ ., data = XYE)
  Response <- predict(Model, newdata = XP, type = "response")
  Predictions[[Nom]] <- as.numeric(Response)
  Time[[Nom]] <- ifelse(is.null(Time[[Nom]]), 0, Time[[Nom]]) + (proc.time() - Start)[3]
  
  #********************* REGULARIZED REGRESSIONS *********************#
  
  print(Nom <- "OLS (GLMNET)")
  Start <- proc.time()
  Model <- glmnet::glmnet(x = XME, y = YME, lambda = 0, alpha = 0, family = "gaussian")
  Response <- predict(Model, newx = XMP, type = "response")
  Predictions[[Nom]] <- as.numeric(Response)
  Time[[Nom]] <- ifelse(is.null(Time[[Nom]]), 0, Time[[Nom]]) + (proc.time() - Start)[3]
  
  print(Nom <- "Ridge (GLMNET)")
  Start <- proc.time()
  Model <- glmnet::cv.glmnet(x = XME, y = YME, alpha = 0, family = "gaussian")
  Response <- predict(Model, s = "lambda.min", newx = XMP, type = "response")
  Predictions[[Nom]] <- as.numeric(Response)
  Time[[Nom]] <- ifelse(is.null(Time[[Nom]]), 0, Time[[Nom]]) + (proc.time() - Start)[3]
  
  # Regularized Regression to reduce the model variance 
  # alpha = 1 for lasso (push some coefficients to 0 for some variables), alpha = 0 for ridge (no coefficients at 0)
  
  # Recall that λ is a tuning parameter that helps to control our model from over-fitting to the training data
  # However, to identify the optimal λ value we need to perform cross-validation (CV)
  # cv.glmnet provides a built-in option to perform k-fold CV, and by default, performs 10-fold CV
  
  # the 10-fold CV mean squared error (MSE) across the λ values
  
  # number of the top = number of variables 
  # The first vertical dashed lines represent the λ value with the minimum MSE 
  # and the second one the largest λ value within one standard error of the minimum MSE
  
  # min(Model$cvm)       # minimum MSE
  # Model$lambda.min     # lambda for this min MSE
  
  # Model$cvm[Model$lambda == Model$lambda.1se]  # 1 st.error of min MSE
  
  #  Model$lambda.1se  # lambda for this MSE
  
  # Influential variables 
  
  # coef(Model, s = "lambda.1se") %>%
  #   tidy() %>%
  #   filter(row != "(Intercept)") %>%
  #   ggplot(aes(value, reorder(row, value), color = value > 0)) +
  #   geom_point(show.legend = FALSE) +
  #   ggtitle("Influential variables") +
  #   xlab("Coefficient") +
  #   ylab(NULL)
  
  print(Nom <- "Lasso (GLMNET)")
  Start <- proc.time()
  Model <- glmnet::cv.glmnet(x = XME, y = YME, alpha = 1, family = "gaussian")
  Response <- predict(Model, s = "lambda.1se", newx = XMP, type = "response")
  Predictions[[Nom]] <- as.numeric(Response)
  Time[[Nom]] <- ifelse(is.null(Time[[Nom]]), 0, Time[[Nom]]) + (proc.time() - Start)[3]
  
  # coef(Model, s=Model$lambda.1se)
  
  Alphas <- c(0.25, 0.5, 0.75)
  
  for(Alpha in Alphas){
    print(Nom <- stringr::str_c("Elastic net (GLMNET|alpha=", Alpha, ")"))
    Start <- proc.time()
    Model <- glmnet::cv.glmnet(x = XME, y = YME, alpha = Alpha, family = "gaussian")
    Response <- predict(Model, s = "lambda.min", newx = XMP, type = "response")
    Predictions[[Nom]] <- as.numeric(Response)
    Time[[Nom]] <- ifelse(is.null(Time[[Nom]]), 0, Time[[Nom]]) + (proc.time() - Start)[3]
  }
  
  #********************* TREE *******************************#
  
  print(Nom <- "Tree (RPART)")
  Start <- proc.time()
  Model <- rpart::rpart(formula = Y ~ ., data = XYE)
  Response <- predict(Model, newdata = XP, type = "vector")
  Predictions[[Nom]] <- as.numeric(Response)
  Time[[Nom]] <- ifelse(is.null(Time[[Nom]]), 0, Time[[Nom]]) + (proc.time() - Start)[3]
  
  # rpart.plot(Model)
  
  #********************* RANDOM FORESTS *********************#
  # tune the number of tree hyperparameter in the cross validation 
  Numbers_Of_Trees <- c( 100, 250, 500)
  
  # make ranger compatible names
  names(XYE) <- make.names(names(XYE), allow = FALSE)
  names(XP) <- make.names(names(XP), allow = FALSE)
  
  for (ntree in Numbers_Of_Trees) {
    
    print(Nom <- stringr::str_c("Random forest (RANDOMFOREST|ntree=", ntree, ")"))
    Start <- proc.time()
    features <- setdiff(names(XYE), "Y")
    Model <- ranger(formula    = Y ~ .,
                    data       = XYE,
                    num.trees  = ntree, # number of trees 
                    mtry       = floor(length(features) / 3), # the number of variables to randomly sample as candidates at each split - usal value for regression = p/3 with p the total number of variables  
                    respect.unordered.factors = 'order',
                    verbose    = FALSE,
                    seed       = 123
    )
    Response <- predict(Model, data = XP, type = "response")
    Response <- Response$predictions
    Predictions[[Nom]] <- as.numeric(Response)
    Time[[Nom]] <- ifelse(is.null(Time[[Nom]]), 0, Time[[Nom]]) + (proc.time() - Start)[3]
  }
  
  #********************* BOOSTING *************************#
  
  # Xgboost - apprx 10x faster than gbm
  # For boosting tree models, the most important parameter is the number of trees to build - nrounds parameter
  # XGBoost only works with matrices that contain all numeric variables
  
  # tune the number of tree hyperparameter in the cross validation 
  Numbers_Of_Trees <-  c(100, 250, 500)
  
  for (nrounds in Numbers_Of_Trees){
    print(Nom <- stringr::str_c("XGBoost|n.trees=", nrounds))
    Model <- xgboost(data = XME, 
                     label = YME,
                     nrounds = nrounds,
                     eta = 0.1, # learning rate 0.3 by default
                     max_depth = 4, #  Maximum depth of a tree. 6 by default
                     objective = "reg:linear",
                     print_every = 1000) # hide results 
    Response <- predict(Model , XMP, missing = NA)
    Predictions[[Nom]] <- as.numeric(Response)
    Time[[Nom]] <- ifelse(is.null(Time[[Nom]]), 0, Time[[Nom]]) + (proc.time() - Start)[3]
  }
  
  # #********************* SVM *****************************#
  # NOT RUN 
  # tune Kernel and Cost hyper-parameters in the cross validation 
  # Kernels <- c("linear", "polynomial", "radial")
  # Costs <- c(0.1, 1, 2)
  # 
  # for(Kernel in Kernels)
  # {
  #   for(Cost in Costs)
  #   {
  #     print(Nom <- stringr::str_c("SVM (e1071|kernel=", Kernel, "|cost=", Cost, ")"))
  #     Start <- proc.time()
  #     Model <- e1071::svm(Y ~ ., data = XYE, kernel = Kernel, cost = Cost)
  #     Response <- predict(Model, newdata = XP, type = "response")
  #     Predictions[[Nom]] <- as.numeric(Response)
  #     Time[[Nom]] <- ifelse(is.null(Time[[Nom]]), 0, Time[[Nom]]) + (proc.time() - Start)[3]
  #   }
  # }
  
  Output[[1 + length(Output)]] <- as.data.table(do.call(cbind, Predictions))
  
  print("**************************************************")
}
```


## Assess cross validation errors 
```{r, message = FALSE, warning = FALSE, echo = TRUE, eval = TRUE}
# Stack all the outputs tables up 

Output <- data.table::rbindlist(l = Output, use.names = TRUE, fill = TRUE)

# Measure execution time 
Time <- data.table(Model = names(Time), Time = unlist(Time))

# Function to define the error metric : Mean Absolute Error 
loss_function <- function(X,Y){
  mean(abs(X-Y))
}

# Assess cross validation errors for each model 
Errors <- apply(X = Output, MARGIN = 2, FUN = loss_function, Y = Output$Y)
Errors <- data.table(Model = names(Errors), error_rate = Errors)
Errors <- merge(x = Errors, y = Time, by = "Model", all.x = TRUE, all.y = FALSE)
Errors <- Errors[order(error_rate)]
Errors

```
> By analyzing the cross validation errors, the best model is Random Forest 250 trees. Let's retrain on the full training set and predict on the testing set! 

# PREDICT ON TEST SET   
## Retrain on the full training set 
```{r, message = FALSE, warning = FALSE, echo = TRUE, eval = TRUE}
# Training set 
X <- as.data.table(df_train %>% select(-Y))
Y <- df_train$Y

XY <- cbind(Y,X)
names(XY)[1] <- "Y"

# Testing set 
X_test <- as.data.table(df_test %>% select(-Y))
Y_test <- df_test$Y

XY_test <- cbind(Y_test, X_test)
names(XY_test)[1] <- "Y"

# make ranger compatible names
names(XY) <- make.names(names(XY), allow = FALSE)
names(X_test) <- make.names(names(X_test), allow = FALSE)

features <- setdiff(names(XY), "Y")

# Best Model: Random Forest 250 trees according to the the cross validation errors 

Model_final<- ranger(formula    = Y ~ .,
                     data       = XY,
                     num.trees  = 250, # nombre d'arbres 
                     mtry       = floor(length(features) / 3), # nombre de variables tirés au hasard - valeur usuelle pour regression = p/3 avec p nombre de variables 
                     respect.unordered.factors = 'order',
                     # To plot variable imortance 
                     importance = "impurity",
                     # We want to access the quantile regressions forest to assess prediction intervals
                     quantreg   = TRUE,
                     verbose    = FALSE,
                     seed       = 42)

```

## Assess performance on the test set
```{r, message = FALSE, warning = FALSE, echo = TRUE, eval = TRUE}

# Predict on the test set
predictions_testRF <- predict(Model_final, data = X_test, type = "response")
predictions_test <- data.frame(cbind(Y_test, predictions_testRF$predictions))

# Performance on the test set
loss_function(X = predictions_testRF$predictions, Y = Y_test)

```
> The Mean Absolute Error equals to 0.58 on the test set. Let's determine the main discriminant variables by plotting the variable importance. 

## Variable Importance
```{r, message = FALSE, warning = FALSE, echo = TRUE, eval = TRUE}
#  Plot Top important variables 

var_imp_ranger<-as.data.frame(Model_final$variable.importance)
variables <-(as.vector((row.names(var_imp_ranger))))
var_imp_ranger <- cbind(variables,var_imp_ranger)
var_imp_ranger <- var_imp_ranger %>% arrange(desc(`Model_final$variable.importance`))


p <- ggplot(var_imp_ranger,
       aes(x = reorder(variables,`Model_final$variable.importance`) ,
           y = `Model_final$variable.importance`, 
           fill = `Model_final$variable.importance`))+ 
  geom_bar(stat="identity", position="dodge", aes(text = `Model_final$variable.importance`))+
  coord_flip()+
  ylab("Importance")+
  xlab("")+
  ggtitle("Variable Importance - Random Forest 500 Trees")+
  guides(fill = F)+
  scale_fill_gradient()+
  theme_classic()

ggplotly(p, tooltip = "text")

```
> The most important variables are **odds**, **elo.diff.fh**, **elo.away.ft** and **diff.probs**. Our feature engineering has therefore increased the model performance! 

> More important than the average values given by the random forests, we want to analyze the quantile predictions to get prediction intervals. We will use them to determine a betting strategy thereafter. 

# OVER-UNDER BETTING STRATEGY 
## Prediction Intervals with Quantile Regression Forests 
```{r, message = FALSE, warning = FALSE, echo = TRUE, eval = TRUE}

# Quantile Predictions 
quantiles_reg_forests <- predict(Model_final, data = X_test, type = "quantiles", quantiles = seq(0, 1, by = 0.1))

pred_intervals <- as.data.table(quantiles_reg_forests$predictions)

# Concatenate actual value (profit) and quantile predictions 
actual_profit_w_pred_intervals <- data.table(cbind(Y_test, pred_intervals))

names(actual_profit_w_pred_intervals)[2:ncol(actual_profit_w_pred_intervals)] <- c("Q0", "Q10","Q20", "Q30", "Q40", "Q50",
                                                                                   "Q60", "Q70","Q80", "Q90", "Q100")

# Display the five first rows 
actual_profit_w_pred_intervals %>% head(5)


```
<br>
> The Y_test value is the real profit of the bet. The other variables are the different **quantile predictions** (deciles in our case) with the Random Forest Model. They give us an idea about the prediction intervals. 

## Decison Rule to place bets 

> **Our betting strategy will be based on quantile predictions**. Given a quantile (eg quantile 10%), the strategy will consider placing only bets where the **predicted quantile 10% values are greater than 0**. It implies that there's a probability of 90% (quantile 10%) that the profit is positive. 

```{r, message = FALSE, warning = FALSE, echo = TRUE, eval = TRUE}

# Function to get the number of bets placed, the proportion of winning/loosing bets, the overall profit for each quantile 

summarise_bets_placed <- function(quantile){
  
  tmp <- copy(actual_profit_w_pred_intervals)
  
  # Distinguish positive profits from negative profits  
  tmp  <- tmp[, positive_profit := ifelse(Y_test > 0, 1, 0)]
  
  tmp <-  tmp[get(quantile) > 0,
              .(nb_bets_placed = .N,
                sum_profit = sum(Y_test)),
              by = .(positive_profit)]
  
  tmp$decision_rule_quantile <- quantile
  
  tmp  <- tmp[,
              c("prop_bets", "sum_profit_quantile") := list(nb_bets_placed/sum(nb_bets_placed), sum(sum_profit)),
              by= .(decision_rule_quantile)]
  
  sdcols <- c("decision_rule_quantile", "positive_profit", "nb_bets_placed", "prop_bets", "sum_profit", "sum_profit_quantile")
  
  tmp <- tmp[, .SD, .SDcols = sdcols]
  
  return(tmp)
  
}

quantiles <- list("Q10", "Q20", "Q30", "Q40", "Q50", "Q60", "Q70", "Q80", "Q90", "Q100")

bets_placed_quantile <- map(quantiles,
                             summarise_bets_placed)

bets_placed_quantile <- rbindlist(bets_placed_quantile)

bets_placed_quantile


```

> This table give us the number of bets to be placed, the proportion of winning/loosing bets and the overall profit for each quantile-based decision rule.  

> **Interpretation** 
<br> 
*Example_1* : Our strategy is to bet over only if Quantile 10% > 0. Only 125 bets will be placed. They are all winning bets with an overall profit of 38.4
<br>
*Example_2* : Our strategy is to bet over only if Quantile 60% > 0. 3, 305 bets will be placed. 2,899 bets are winning and 406 loosing. But the overall profit (1895.4) is higher than in *Example_1* 
<br>
*Example_3* : Our strategy is to bet over if Quantile 100% > 0. Thus, all the bets will be placed. There is no selection! 7,761 bets with 3,558 winning bets and 4,203 loosing bets. The overall profit is negative: -350.4 

<br>
> According to his risk aversion, the gambler can choose between: 
<br> 
1. Mitigate the risk by placing very few bets and securing the profits - Decision Rule:  Quantile 10% > 0
<br>
2. Try to optimize the overall profit - Decsion Rule:  Quantile 50% > 0 or Quantile 60%  > 0. In such a case, there will be loosing bets but the overall profit seems to be higher. 

> Let's apply our strategy on another random sample from test set to check the **robustness of the strategy**

##Strategy Robustness

```{r, message = FALSE, warning = FALSE, echo = TRUE, eval = TRUE}

# Random sample from test set
set.seed(42) # for reproducibility 

size <- 2500
ind <- sample(1:nrow(X_test), size)
X_test_samp <- X_test[ind]
Y_test_samp <- Y_test[ind]
sum(Y_test_samp)

# Predict on the test set
quantiles_reg_forests <- predict(Model_final, data = X_test_samp, type = "quantiles", quantiles = seq(0, 1, by = 0.1))

pred_intervals <- as.data.table(quantiles_reg_forests$predictions)

actual_profit_w_pred_intervals <- data.table(cbind(Y_test_samp, pred_intervals))

names(actual_profit_w_pred_intervals) <- c("Y_test","Q0", "Q10","Q20", "Q30", "Q40", "Q50","Q60", "Q70","Q80", "Q90", "Q100")

quantiles <- list("Q10", "Q20", "Q30", "Q40", "Q50", "Q60", "Q70", "Q80", "Q90", "Q100")

bets_placed_quantile_samp <- map(quantiles,
                                 summarise_bets_placed)

bets_placed_quantile_samp <- rbindlist(bets_placed_quantile_samp)

bets_placed_quantile_samp

```

> If our strategy is to bet over if Quantile 10% > 0: there are 43 bets placed (over 2,500 possible bets) and we win 13.08
<br> Here again, the best strategy seems to bet over Quantile > 60%. 1325 bets placed:  1049 winning and 276 loossing bets. The overall profit is 612.2 

> Out of intellectual curiosity, let's consider the worst case scenario: we only keep bets with negative profit 
<br> What would be the results of our strategy based on quantiles? 

##Worst Case Scenario 

```{r, message = FALSE, warning = FALSE, echo = TRUE, eval = TRUE}

# Worst Case Scenario - we only keep bets with negative profit  
ind <- which(Y_test < 0)
X_test_wc <-  X_test[ind]
Y_test_wc <- Y_test[ind]

# Quuntile Predictions with Random Forest  
quantiles_reg_forests <- predict(Model_final, data = X_test_wc, type = "quantiles", quantiles = seq(0, 1, by = 0.1))

pred_intervals <- as.data.table(quantiles_reg_forests$predictions)

actual_profit_w_pred_intervals <- data.table(cbind(Y_test_wc, pred_intervals))

names(actual_profit_w_pred_intervals) <- c("Y_test","Q0", "Q10","Q20", "Q30", "Q40", "Q50","Q60", "Q70","Q80", "Q90", "Q100")

quantiles <- list("Q10", "Q20", "Q30", "Q40", "Q50", "Q60", "Q70", "Q80", "Q90", "Q100")

bets_placed_quantile_samp <- map(quantiles,
                                 summarise_bets_placed)

bets_placed_quantile_samp <- rbindlist(bets_placed_quantile_samp)

bets_placed_quantile_samp

```

> Even in this worst case scenario, a risk-averse gambler who only bet over if Quantile 10% > 0 will loose very little money since there is only 1 bet placed. Thus, our strategy can be used to mitigate the risk and to avoid significant financial losses. 
